---
title: "Daily discharge within the last month"
author: "Phil Savoy"
date: "Last updated on `r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    df_print: paged
    number_sections: true
    theme:
      bg: "#2E3440"
      fg: "#ECEFF4"
      primary: "#5E81AC"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding) })
---

```{r, include=F}
#===============================================================================
#Setup
#===============================================================================
#Set global chunk options
  knitr::opts_chunk$set(
    message=F, 
    warning=F,
    echo=F
  )

#Decimal display
  options(scipen = 10000)
  
#Read in data from the pipeline
  tar_load(gauges)
  tar_load(daily_discharge)
  tar_load(huc_wgs84)
```

# Map of locations and discharge data

Below is a linked map of locations actively reporting discharge within the past 30 days and the corresponding plots of discharge time series.

```{r, include=F}
#===============================================================================
#Link data with crosstalk
#===============================================================================
gauges_share <- SharedData$new(
  gauges, 
  key = ~monitoring_location_id, 
  group = "group"
)

disch_share <- SharedData$new(
  daily_discharge, 
  key = ~monitoring_location_id, 
  group = "group"
)
```


```{r, include=FALSE}
#===============================================================================
#Make plots of daily discharge
#===============================================================================
#Make initial static map
  discharge_plot <- ggplot(data = disch_share, aes(x = time, y = value)) + 
    geom_line(color = "#4c566a", alpha = 0.5) +
  
    #Theme elements
    ylab("Discharge (cubic feet per second)") +
    xlab("Time") +
    theme_classic() +
    theme(
      axis.title = element_text(color = "#D9DCE2"),
      axis.text = element_text(color = "#D9DCE2"),
      axis.line = element_line(size = 2, color="black"),
      axis.ticks = element_line(size = 2, color="black"),
      plot.background = element_rect(fill = "transparent"),
      panel.background = element_rect(fill = "#F9F9F9")
    )

#Convert to interactive
  discharge_html <- ggplotly(discharge_plot) %>% 
    highlight(
      on = "plotly_hover",
      off = "plotly_doubleclick", 
      color = "#4c566a"
    )
```


```{r, include=F}
#===============================================================================
#Map of HUC and active gauges
#===============================================================================
map_html <- leaflet(gauges_share) %>% 
  #Add background tiles
  addProviderTiles(providers$CartoDB.Positron) %>% 
  
  #HUC boundary
  addPolygons(
    data = huc_wgs84, 
    fillColor = "#4c566a",
    fillOpacity = 0.1,
    color = "#4c566a"
  ) %>% 
  addCircleMarkers(
    fillColor = "#4c566a",
    fillOpacity = 1,
    radius = 4,
    stroke = FALSE,
    popup = ~htmlEscape(sprintf("ID: %s", monitoring_location_id))
  ) 
```


```{r, fig.height=4, fig.width=6}
#===============================================================================
#Combine into final plot
#===============================================================================
bscols(
  widths = c(12, 12),
  map_html, 
  discharge_html
)
```


# Basic site information

A basic table of site information about the unique location id, the site name, and the site type. Additionally, it shows the breakdown of how much of the data is still in a provisional versus approved status.

```{r, include=F}
#===============================================================================
#Get breakdown of approval status by locaiton
#===============================================================================
approved_breakdown <- daily_discharge %>% 
  #Calculate percentage of approvate data by location
  sf::st_drop_geometry() %>% 
  group_by(monitoring_location_id, approval_status) %>% 
  summarise(n = n()) %>%
  mutate(percent = n / sum(n) * 100)  %>% 
  
  #Pivot wide
  tidyr::pivot_wider(
    id_cols = monitoring_location_id, 
    names_from = approval_status, 
    values_from = c("percent")
  )
```


```{r}
#===============================================================================
#Table of basic site information
#===============================================================================
  gauges %>%
    sf::st_drop_geometry() %>% 
    inner_join(approved_breakdown) %>% 
    kbl(
      caption = "Gauges with daily data in the past 30 days"
    ) %>%
    kable_styling(bootstrap_options = c("striped"))

```

