---
title: "Daily discharge within the last month"
author: "Phil Savoy"
date: "Last updated on `r format(Sys.time(), '%d %B, %Y, %H:%M')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    df_print: paged
    number_sections: true
    theme:
      bg: "#2E3440"
      fg: "#ECEFF4"
      primary: "#5E81AC"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding) })
---

```{r, include=F}
#===============================================================================
#Setup
#===============================================================================
#Set global chunk options
  knitr::opts_chunk$set(
    message=F, 
    warning=F,
    echo=F
  )

#Decimal display
  options(scipen = 10000)
  
#Read in data from the pipeline
  tar_load(gauges_wgs84)
  tar_load(daily_discharge)
  tar_load(counties_wgs84)
  tar_load(state_wgs84)
```

# Map of locations and discharge data

Below is a linked map of locations actively reporting discharge within the past 30 days and the corresponding plots of discharge time series.

```{r, include=F}
#===============================================================================
#Link data with crosstalk
#===============================================================================
gauges_share <- SharedData$new(
  gauges_wgs84, 
  key = ~monitoring_location_id, 
  group = "group"
)

disch_share <- SharedData$new(
  daily_discharge, 
  key = ~monitoring_location_id, 
  group = "group"
)
```


```{r, include=FALSE}
#===============================================================================
#Make plots of daily discharge
#===============================================================================
#Make initial static map
  discharge_plot <- ggplot(data = disch_share, aes(x = time, y = value)) + 
    geom_line(color = "#4c566a", alpha = 0.5) +
  
    #Theme elements
    ylab("Discharge (cubic feet per second)") +
    xlab("Time") +
    theme_classic() +
    theme(
      axis.title = element_text(color = "#D9DCE2"),
      axis.text = element_text(color = "#D9DCE2"),
      axis.line = element_line(linewidth = 2, color="black"),
      axis.ticks = element_line(linewidth = 2, color="black"),
      plot.background = element_rect(fill = "transparent"),
      panel.background = element_rect(fill = "#F9F9F9")
    )

#Convert to interactive
  discharge_html <- ggplotly(discharge_plot) %>% 
    highlight(
      on = "plotly_hover",
      off = "plotly_doubleclick", 
      color = "#4c566a"
    )
```


```{r, include=F}
#===============================================================================
#Map of HUC and active gauges
#===============================================================================
map_html <- leaflet(gauges_share) %>% 
  #Add background tiles
  addProviderTiles(providers$CartoDB.Positron) %>% 
  
  #Add points
  addCircleMarkers(
    fillColor = "#4c566a",
    fillOpacity = 1,
    radius = 4,
    stroke = FALSE,
    popup = ~htmlEscape(sprintf("ID: %s", monitoring_location_id))
  ) 
```


```{r, fig.height=4, fig.width=6}
#===============================================================================
#Combine into final plot
#===============================================================================
bscols(
  widths = c(12, 12),
  map_html, 
  discharge_html
)
```


# Basic site information

A basic table of site information about the unique location id, the site name, and the site type. Additionally, it shows the breakdown of how much of the data is still in a provisional versus approved status.

```{r, include=F}
#===============================================================================
#Get breakdown of approval status by locaiton
#===============================================================================
approved_breakdown <- daily_discharge %>% 
  #Calculate percentage of approvate data by location
  sf::st_drop_geometry() %>% 
  group_by(monitoring_location_id, approval_status) %>% 
  summarise(n = n()) %>%
  mutate(percent = n / sum(n) * 100)  %>% 
  
  #Pivot wide
  tidyr::pivot_wider(
    id_cols = monitoring_location_id, 
    names_from = approval_status, 
    values_from = c("percent")
  )
```


```{r}
#===============================================================================
#Define custom reactable theme
#===============================================================================
my_theme <- function(font_size = 14, font_color = "#ECEFF4", header_font_size = 15,
  header_font_color = "#ECEFF4", background_color = "#2E3440", cell_padding = 6,
  centered = FALSE){

  if(!is.logical(centered)){
    stop("`centered` must be TRUE or FALSE")
  }

  if(centered == TRUE){
    centered_content = list(display = "flex", flexDirection = "column", justifyContent = "center")
  } else {centered_content = NULL}

  reactableTheme(
    cellStyle = centered_content,
    color = font_color,
    backgroundColor = background_color,
    borderColor = "#ECEFF4",
    borderWidth = "1px",
    stripedColor = "#d8dee9",
    highlightColor = "#d8dee9",
    cellPadding = cell_padding,
    tableStyle = list(fontSize = font_size),
    headerStyle = list(
      borderWidth = "2px",
      color = header_font_color,
      transitionDuration = "0.5s",
      "&:hover[aria-sort]" = list(color = "#ECEFF4"),
      "&[aria-sort='ascending'], &[aria-sort='descending']" = list(color = "#ECEFF4"),
      fontSize = header_font_size
    ),
    groupHeaderStyle = list(
      "&:not(:empty)" = list(color = font_color, fontSize = header_font_size),
      "&:hover" = list(
        fontWeight = "bold",
        transitionDuration = "1s",
        transitionTimingFunction = "ease-out",
        color = "#d8dee9"
      )
    ),
    searchInputStyle = list(
      backgroundColor = "#ECEFF4",
      color = "#212529",
      borderColor = "#222222",
      "&:focus" = list(color = "#212529")
    ),
    inputStyle = list(backgroundColor = "#ECEFF4", color = "#212529"),
    rowSelectedStyle = list(backgroundColor = "#2E3440", color = "#ECEFF4"),
    selectStyle = list(
      backgroundColor = "#81a1c1",
      color = "#ECEFF4",
      borderColor = "#ECEFF4",
      outlineColor = "#ECEFF4",
      "&:hover" = list(backgroundColor = "#88c0d0")
    ),
    pageButtonStyle = list(
      backgroundColor = "#81a1c1",
      color = "#ECEFF4",
      "&:hover" = list(backgroundColor = "#88c0d0")
    ),
    pageButtonHoverStyle = list(backgroundColor = "#88c0d0", color = "#ECEFF4"),
    pageButtonActiveStyle = list(backgroundColor = "#88c0d0", color = "#ECEFF4"),
    pageButtonCurrentStyle = list(backgroundColor = "#88c0d0", color = "#ECEFF4")
  )
}
```


```{r}
#===============================================================================
#Table of basic site information
#===============================================================================
gauges_wgs84 %>%
  #Drop geometry and join
  sf::st_drop_geometry() %>% 
  inner_join(approved_breakdown) %>% 

  #Make table
  reactable(
    defaultPageSize = 15,
    theme = my_theme(font_size = 9, header_font_size = 9)
  ) 

```

# Data support

```{r}
#===============================================================================
#Get count of gauges and records per county
#===============================================================================
#Spatially join gauges with counties
  gauge_county_wgs84 <- sf::st_join(
    gauges_wgs84, 
    counties_wgs84, 
    join = st_intersects
  ) 
      
#Drop the geometry
  gauge_county <- gauge_county_wgs84 %>% 
    #Drop geometry
    sf::st_drop_geometry() %>% 
    select(-ID)
    
#Number of gauges per county
  gauge_count <- gauge_county %>% 
    group_by(county) %>% 
    count() %>% 
    rename(gauges = n) %>% 
    data.frame()
  
#Number of days of 
  record_count <- daily_discharge %>% 
    #Join with county data
    left_join(., gauge_county, by = "monitoring_location_id")  %>% 
    
    #Get number of records by county
    group_by(county) %>% 
    count() %>% 
    rename(daily_records = n) %>% 
    data.frame()

#Merge in gauge and record count
  county_counts_wgs84 <- merge(
    merge(
      counties_wgs84, 
      gauge_count,
      by = "county"
    ),
    record_count,
    by = "county"
  )
```


```{r}
#===============================================================================
#Reproject based on UTM zone for state centroid
#===============================================================================
#Get centroid, I know it is not exact because of geometric coordinates
  centroid <- sf::st_centroid(state_wgs84) 
  
#Get UTM zone
  utm_zone <- (floor((st_coordinates(centroid)[, "X"] + 180)/6) %% 60) + 1

#Define projection string
  state_proj <- paste0("+proj=utm +zone=", utm_zone," ellps=WGS84")

#Reproject into UTM
  state_utm <- sf::st_transform(state_wgs84, state_proj)  
  county_counts_utm <- sf::st_transform(county_counts_wgs84, state_proj)  
```


```{r}
#===============================================================================
#Prepare maps
#===============================================================================
#Define a base plot
  base_plot <- ggplot() + 
    #State outline
    with_outer_glow(
      geom_sf(data = state_utm, color = "black", alpha = 0.8),
      colour = "black", 
      sigma = 3
    ) + 
  
    #Theme elements
    guides(fill = guide_colourbar(barwidth = 6, barheight = 1)) +
    theme_classic() +
    theme(
      text = element_text(size = 9, color = "#F9F9F9"),
      legend.position = "bottom",
      legend.background = element_rect(
        fill = "#2E3440", 
        size = 0.5,
        linetype = "solid"
      ),
      axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      panel.background = element_rect(fill = "#2E3440", colour = NA), 
      plot.background = element_rect(fill = "#2E3440", colour = NA)
    )    
    
    
#Number of gauges
  gauge_plot <- base_plot + 
    #County level summary
    geom_sf(data = county_counts_utm, aes(fill = gauges)) + 
    scale_fill_gradient(
      low = "#eceff4",
      high = "#bf616a",
      ""
    ) +
    ggtitle("Number of gauges")

#Number of days of data
  records_plot <- base_plot + 
    #County level summary
    geom_sf(data = county_counts_utm, aes(fill = daily_records)) + 
    scale_fill_gradient(
      low = "#eceff4",
      high = "#bf616a",
      ""
    ) +
    ggtitle("Number of daily records")
```



```{r, dev = "png", dev.args=list(bg="transparent")}
ggpubr::ggarrange(gauge_plot, records_plot)
```
